---
title: "Live Assignment 7"
author: "Chris Donlan"
date: "November 7, 2016"
output: md_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Part B
Per the instruction, Part B was completed first. This function takes a single numeric argument and convert the number from base 10 to base 7. Function returns numeric results.
```{r }
#part B
base10to7<-function(x){
  
  if(!is.numeric(x))
    stop("Argurment must be numeric")
  
  i=0
  sum=0
  while(x%/%7!=0){
    sum<-sum+((x%%7)*(10^i))
    i=i+1
    x<-x%/%7
  }
  sum<-sum+((x%%7)*(10^i))
  return(sum)
}
```

##Part A
This function takes a single numeric argument and counts up to that number in base 7. Function returns numeric results.
```{r }
#part A
p7 <-function(x) 
{
  if(!is.numeric(x))
    stop("Argurment must be numeric")
  
  results <- c()
  i = 0
  
  while(i < x)
  {
    results <- c(results,base10to7(i))
    i <- i +1
  }
  
  return(results)
}
```

##Part C
This function takes a single numeric argrument and converts it from base 7 to base 10. Function returns numeric results.
```{r }
#part C
base7to10 <- function(x){
  
  if(!is.numeric(x))
    stop("Argurment must be numeric")
  
  y <-nchar(x)
  result = 0
  for(i in 1:y)
  {
    #print(y)
    digit <- as.numeric(substr(x,(y-i+1),(y-i+1)))
    #print(digit)
    converted <-digit*(7^(i-1))
    
    #print(converted)
    result <- result + converted
  }
  
  return(result)
}

```

##Part D
This function takes two numeric arguments. The first argument, is the base which is being convert from to base base 10. The second argument, is the number which is being converted. Function returns numeric results.
```{r }

#part D
baseKto10 <- function(k,x){
  
  if(!is.numeric(k))
    stop("First argurment must be numeric")
  
  if(!is.numeric(x))
    stop(" Second argurment must be numeric")
  
  xchar <-nchar(x)
  result = 0
  for(i in 1:xchar)
  {
    #print(y)
    digit <- as.numeric(substr(x,(xchar-i+1),(xchar-i+1)))
    #print(digit)
    converted <-digit*(k^(i-1))
    
    #print(converted)
    result <- result + converted
  }
  
  return(result)
}
```